\TheTitle

### 2017-06-28 paper/methodology.tex
Methodology participants and question answers
Adding the number of participants and the answers to the study
questions.

In order to determine the effectiveness of the merge-tree model on
comprehension and summarization of git repositories, we conducted a user
study on \evantodo{NUMBER} participants. The user study is a
mixed-methods study, but with more focused on the quantitative aspects.
We chose to use a mixed-methods approach to determine both if the model
is able to improve the time performance and accuracy of the
participants, and if the participants found the merge trees more
enjoyable for the given tasks.

@@

% TODO: Show this in the introduction maybe

% It is worth noting that in the fourth
% quartile, the size of the tree drops off quickly from the top tree, with
% the next tree containing only 4708 nodes, and the third largest tree
% containing only 2349 commits.

Using this technique, we selected commit
\emph{8eb88c80d444fd249edaa7d895666cde79e7b3b8} from the tree containing
a single node (Figure~\ref{fig:commit_1}), and commit
\emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe}, from the tree
containing seven nodes (Figure~\ref{fig:commit_2}).

@@

>>>>

In order to determine the effectiveness of the merge-tree model on
comprehension and summarization of git repositories, we conducted a user
study on 12 participants. The user study is a
mixed-methods study, but with more focused on the quantitative aspects.
We chose to use a mixed-methods approach to determine both if the model
is able to improve the time performance and accuracy of the
participants, and if the participants found the merge trees more
enjoyable for the given tasks.

@@

% TODO: Show this in the introduction maybe
% It is worth noting that in the fourth
% quartile, the size of the tree drops off quickly from the top tree, with
% the next tree containing only 4708 nodes, and the third largest tree
% containing only 2349 commits.

% TODO: Fix this, the commit hash is wrong.
Using this technique, we selected commit
\emph{a3c1239eb59c0a907f8be5587d42e950f44543f8} from the tree containing
a single node (Figure~\ref{fig:commit_1}), which we will refer to as
\comA, and commit \emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe}, from
the tree containing seven nodes (Figure~\ref{fig:commit_2}), which we
will refer to as \comB.

@@

\subsection{Data Extraction}
\label{sub:data_extraction}

The study is recorded using screen capture and audio capture software
for further analysis. From the resulting videos, we are able to extract
the timing and accuracy of each participant over each task. We record
the timing, accuracy, task, commit, and tool used for each part. We also
record some addition information about whether the participant was
correct, guessing, partially correct, or completely wrong, as this may
provide some interesting insights.

The answers to each question is relatively straight-forward, as we can
extract the information directly from gitk and Linvis. Measuring the
accuracy of the questions is more challenging. In the question regarding
the merges leading to the merging of a given commit, both the merges and
the ordering of the merges matter.

The correct answers for \comA are shown in
Table~\ref{tab:coma_study_answers}, and the correct answers for \comB are
shown in Table~\ref{tab:comb_study_answers}.

\begin{table}[htpb]
  \centering
  \caption{Answers to the question from the conceptual and summarization portions of the user study for \comA}
  \label{tab:coma_study_answers}
  \begin{tabular}{l|l}
    Question                                              & Answer \\\hline\hline
    Number of commits in the merge tree                   & 1\\
    Number of merges in the merge tree                    & 1\\\hline
    Merges merging this commit into the master branch     & 1 (11df586407)\\
    Other commits that are merged in the same tree        & None\\
    How many authors are involved with this tree?         & 1\\
    Who contributed the most changes to this merge tree   & David\\
    How many files are modified in this merge tree        & 2\\
    Which file(s) had the most changes in this merge tree & both (pzl.c, asl.c)\\
    Which modules does this merge tree involve & wusb
  \end{tabular}
\end{table}

\begin{table}[htpb]
  \centering
  \caption{Answers to the question from the conceptual and summarization portions of the user study for \comB}
  \label{tab:comb_study_answers}
  \begin{tabular}{l|l}
    Question & Answer \\\hline\hline
    Number of commits in the merge tree & 5 \\
    Number of merges in the merge tree & 3\\\hline
    Merges merging this commit into the master branch     & (219b22b245
    \\
    & $\rightarrow$ \\
    & 8eb88c80d4)\\
    Other commits that are merged in the same tree        & ec4e86ba06\\
    & 9a3f371e99\\
    & 1c85cc6445\\
    & 7c2dfee848\\
    How many authors are involved with this tree?         & 4\\
    Who contributed the most changes to this merge tree   & Randy Dunlap\\
    How many files are modified in this merge tree        & 6\\
    Which file(s) had the most changes in this merge tree & pcm\_lib.c\\
    Which modules does this merge tree involve            & ALSA\\
  \end{tabular}
\end{table}

Extracting the timing information is prone to some issues with where the
duration of answering should start and stop. We try to eliminate these
issues by maintaining the following conventions; the answer duration
begins at the end of the last word of the prompt. The duration ends
immediately before the first word of the final modification to the
answer. Many answers are able to be answered in a single word or phrase,
but some may require multiple sentences that are broken by additional
processing by the participant. An Example of questions where the answer
may be interleaved with solving the task is the task asking the user to
provide the merges on the path from the commit into the master branch.
The goal of this is to eliminate the duration required to provide the
prompt, and eliminate the time required to provide the answer.
